---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# nzpullover

[![Travis-CI Build Status](https://travis-ci.org/nacnudus/nzpullover.svg?branch=master)](https://travis-ci.org/nacnudus/nzpullover) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/nacnudus/nzpullover?branch=master&svg=true)](https://ci.appveyor.com/project/nacnudus/nzpullover) ![Cran Status](http://www.r-pkg.org/badges/version/nzpullover) ![Cran Downloads](https://cranlogs.r-pkg.org/badges/nzpullover)

The nzpullover package makes available road policing data from the New Zealand
Police in a convenient 'tidy' form.  Offence categories include speed, alcohol,
red light, restraints (seatbelts), mobile phone, fleeing drivers, and speeding
police vehicles.

The original data published by the New Zealand Police is available as a
spreadsheet here:
[http://www.police.govt.nz/about-us/publication/road-policing-driver-offence-data-january-2009-september-2016](http://www.police.govt.nz/about-us/publication/road-policing-driver-offence-data-january-2009-september-2016).

The spreadsheet data has been made tidy by using the
[tidyxl](https://github.com/nacnudus/tidyxl)
[unpivotr](https://github.com/nacnudus/unpivotr) packages.  See the scripts in
[/data-raw](https://github.com/nacnudus/nzpullover/tree/master/data-raw).
Zipped csv files are available in
[/inst/extdata](https://github.com/nacnudus/nzpullover/tree/master/inst/extdata).

The New Zealand Police refresh the data approximately quarterly.  If this
package lags behind, then please open an issue
[https://github.com/nacnudus/nzpullover/issues](https://github.com/nacnudus/nzpullover/issues).

## Installation

You can install nzpullover from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("nacnudus/nzpullover")
```

## Example

```{r example, echo = FALSE, fig.width = 9, fig.show = "hold"}
library(nzpullover)
library(tidyverse)
library(forcats)

plotdata <-
  excess %>%
  mutate(series = fct_recode(series,
                             `Officer-issued` = "Officer-issued excess speed band",
                             `Camera-issued` =  "Camera-issued excess speed band")) %>%
  filter(series %in% c("Officer-issued",
                       "Camera-issued")) %>%
  group_by(series, month, speed) %>%
  summarise(value = sum(value)) %>%
  group_by(series, month) %>%
  mutate(prop = value / sum(value),
         cumprop = cumsum(prop))

plotdata %>%
  ggplot(aes(speed, value, colour = month)) +
  geom_point(shape = "-", size = 20) +
  scale_colour_continuous(name = "", trans = "date") +
  scale_y_continuous(labels = scales::comma) +
  facet_wrap(~series, nrow = 1) +
  ggtitle("New Zealand summer speed limit infringements/offences",
          subtitle = "Frequency in each speed band") +
  xlab("Speed band (km/h over the limit)") +
  ylab("Frequency")

plotdata %>%
  ggplot(aes(speed, cumprop, colour = month)) +
  geom_point(shape = "-", size = 20) +
  scale_colour_continuous(name = "", trans = "date") +
  scale_y_continuous(labels = scales::percent) +
  facet_wrap(~series, nrow = 1) +
  ggtitle("New Zealand summer speed limit infringements/offences",
          subtitle = "Cumulative proportion in each speed band") +
  xlab("Speed band (km/h over the limit)") +
  ylab("Cumulative proportion")
```

```{r, echo = TRUE}
glimpse(driving_offences)
glimpse(excess)
glimpse(fleeing_area)
glimpse(fleeing_district)
glimpse(police_speeding)
```
